R Notebook for MSDepression Project

### 2022-09-29 lab_notebook/lab_notebook.Rmd
Add files via upload

>>>>

#### 20220921

[x] replicated!
[x] Updated the stats in my markdown and changed the name to reflect that it is post replication
[x] big changes - correcting the volume multiplication error
[x] Also changed the effect size by volume plot to be scaled logarithmicly
  [x] Now p value of this regression is 0.0187 (Adjusted R2 0.06).
  [x] Elizabeth thinks we can drop the Boot. Ted??
[x] colors for depressed vs nondepressed plots
[x] figure alternatives (move interaction to figure 4, and have fig 5 just brain + scatter)

#### 20220922

[x] no cerebellum -> should I find a way to do a flat representation? (NO)

Need to install python and pennlinc toolkit - did not work. It is broken. Don't use it

#### 20220930 or next week
[] add post hoc */bars to figure 4
[] add legend
[] call it a win!
[] add statistics to other graphs (p/effect size)
